\begin{document}

% --- HEADER ---
\begin{center}
    {\Huge \textbf{Jane Doe}} \\ \vspace{5pt}
    (123) 456-7890 $|$ \href{mailto:jane.doe@email.com}{\url{jane.doe@email.com}} $|$ 
    \href{https://www.linkedin.com/in/janedoe}{\url{linkedin.com/in/janedoe}} $|$ 
    \href{https://github.com/janedoe}{\url{github.com/janedoe}}
\end{center}

% --- EDUCATION ---
\ressection{Education}
\textbf{State University} \hfill Anytown, USA \\
\textit{Bachelor of Science in Computer Science}, Minor in Mathematics \hfill May 2025 \\
GPA: 3.8/4.0

% --- TECHNICAL SKILLS ---
\ressection{Technical Skills}
\begin{itemize*}{\itemsep=0pt \topsep=0pt}
    \item \textbf{Languages:} Python, Java, JavaScript, TypeScript, SQL, C++, Bash
    \item \textbf{Frameworks \& Libraries:} React.js, Node.js, Express.js, Flask, Spring Boot, JUnit, Pytest, Selenium
    \item \textbf{Databases:} PostgreSQL, MongoDB, Redis, MySQL
    \item \textbf{Developer Tools:} Git, Docker, Jenkins, Postman, Visual Studio Code, IntelliJ IDEA
    \item \textbf{Cloud \& DevOps:} AWS (EC2, S3, Lambda, RDS), Google Cloud Platform (GCP), Terraform, Kubernetes, CI/CD
\end{itemize*}

% --- EXPERIENCE ---
\ressection{Experience}
\textbf{Innovate Tech Inc.} \hfill Anytown, USA \\
\textit{Software Engineer Intern} \hfill May 2024 -- Aug 2024
\begin{itemize*}{\itemsep=0pt \topsep=0pt}
    \item Developed and deployed a RESTful API using Spring Boot and Java to manage user data, improving data retrieval times by 20\%.
    \item Wrote comprehensive unit and integration tests using JUnit and Mockito, increasing code coverage of the user service module from 75\% to 92\%.
    \item Collaborated with a team of 5 engineers in an Agile environment, participating in daily stand-ups, sprint planning, and code reviews.
    \item Created a CI/CD pipeline using Jenkins and Docker to automate the build, test, and deployment process for the microservice.
\end{itemize*}

% --- PROJECTS ---
\ressection{Projects}
\textbf{CloudStream Analytics | Full-Stack Web Application} \hfill \textit{Python, Flask, React, PostgreSQL, Docker, AWS}
\begin{itemize*}{\itemsep=0pt \topsep=0pt}
    \item Engineered a full-stack web application to analyze and visualize streaming data from a public API.
    \item Built a Python/Flask backend to process data and serve it via a REST API, deployed as a Docker container on AWS EC2.
    \item Designed a responsive user interface with React.js to display real-time charts and data tables.
    \item Managed data persistence using a PostgreSQL database hosted on AWS RDS.
\end{itemize*}
\vspace{5pt}
\textbf{Distributed File System | Systems Design Project} \hfill \textit{Java, gRPC}
\begin{itemize*}{\itemsep=0pt \topsep=0pt}
    \item Implemented a simplified, fault-tolerant distributed file system in Java with a central metadata server and multiple chunk servers.
    \item Utilized gRPC for efficient, low-latency communication between the client, metadata server, and chunk servers.
    \item Designed a chunking and replication strategy to ensure data availability and durability in case of server failure.
\end{itemize*}

\end{document}