\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\huge \scshape \vspace{6px} Raajveer Khattar} \\
    \small (623) 755-3499 $|$ \href{mailto:rkhatta1@asu.edu}{\underline{rkhatta1@asu.edu}} $|$ \href{https://github.com/rkhatta1/}{\underline{GitHub}} $|$ \href{https://linkedin.com/in/raajveer-khattar/}{\underline{LinkedIn}} $|$ \href{https://rkhatta1.github.io/rkhatta1/}{\underline{Website}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Arizona State University $|$ MS, Computer Software Engineering}}{\footnotesize GPA 3.78 $|$ Jan 2024 - Dec 2025}
      \resumeItemListStart
        \resumeItem{\footnotesize Relevant Coursework: Agile and Lean Engineering, DevOps, MLOps, Cloud Computing, Microservices, CI/CD, Advanced Data Structures, Software Design Patterns, Big Data, and Agentic AI.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECT EXPERIENCE-----------
\section{Project Experience}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{ChapGen -- AI YouTube chapter generator}}{\href{https://github.com/rkhatta1/ChapterGen}{\footnotesize GitHub} $|$ \href{https://chapgen.app}{\footnotesize Live App}}
      \resumeItemListStart
        \resumeItem{Architected and deployed a full-stack, cloud-native application on Google Cloud, orchestrating a suite of 9 microservices with Kubernetes (K3s) to create a resilient, scalable backend.}
        \resumeItem{Engineered a serverless, GPU-accelerated transcription worker using Google Cloud Run; this event-driven design reduced idle infrastructure costs by over 99\% compared to an always-on VM by scaling to zero.}
        \resumeItem{Developed an asynchronous, message-driven workflow using Kafka (Strimzi) as the central message bus, ensuring high throughput and decoupling the ingestion, transcription, and AI-powered chapter generation services.}
        \resumeItem{Configured an Nginx Ingress controller and automated public SSL certificate provisioning with cert-manager and Let's Encrypt, while solving complex, real-world networking and authentication issues across the full cloud stack.}
      \resumeItemListEnd
    \resumeProjectHeading
        {\textbf{SplitThat -- AI accelerated aggregator for Splitwise}}{\href{https://github.com/rkhatta1/splitthat}{\footnotesize GitHub}}
        \resumeItemListStart
            \resumeItem{Architected and developed a full-stack, AI-driven web application using Python (FastAPI) and React to automate the itemization and splitting of expenses from receipt images and PDFs.}
            \resumeItem{Engineered a multimodal AI pipeline with Google Gemini that interprets both visual data and natural language prompts (e.g., "Alice gets the soda") to automatically parse and assign items, improving user efficiency.}
            \resumeItem{Implemented a secure backend with a PostgreSQL database, featuring a full OAuth2 authentication flow with Splitwise and a JWT-based system for persistent user sessions and secure API access.}
            \resumeItem{Developed a robust expense management feature that intelligently creates or updates existing entries in Splitwise via its REST API, preventing duplicate records and ensuring data integrity.}
        \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{The Versus Project -- AI powered football content agent}}{\href{https://github.com/rkhatta1/TheVersusProject}{\footnotesize GitHub} $|$ \href{https://www.youtube.com/watch?v=-R9WLOhUsWE}{\footnotesize Demo Video}}
      \resumeItemListStart
        \resumeItem{Engineered a full-stack news aggregation platform using Python (Flask), React, and PostgreSQL, containerized with Docker for consistent development and deployment environments.}
        \resumeItem{Architected a dual-LLM pipeline; utilized the Gemini API for building context with dynamic news sources and a \href{https://huggingface.co/raajveerk/llama-3.1-8b-versus-caption-v1.0}{\underline{fine-tuned Llama-3.1 model}} for writing @versus style captions.}
        \resumeItem{Implemented a robust PostgreSQL backend with caching, to log all processed news, eliminating 100\% of redundant data fetching and AI processing.}
        \resumeItem{Configured the fine-tuned model to be set up on Kaggle, connected to the backend via a secure ngrok tunnel, showcasing practical MLOps and inference deployment skills.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\small Software Development Engineer, Backend}{\small February 2023 -- December 2023}
      {\footnotesize Trade Journal Project}{\footnotesize Gujarat, India}
      \vspace{-1pt}
      \resumeItemListStart
        \resumeItem{Developed and maintained key backend services for a financial trading platform using a Python (Flask) microservice architecture with robust RESTful API design.}
        \resumeItem{Implemented a new feature for tracking and visualizing trade data, improving user engagement by 15\% and enhancing the platform's core functionality.}
        \resumeItem{Demonstrated effective communication skills while collaborating on templating engines such as Jinja and performed API testing to troubleshoot and validate data integrity across system integrations, further improving the user experience.}
        \resumeItem{Established comprehensive integration and regression test suites using Pytest and Selenium within an agile workflow managed on Jira, ensuring software quality and reliability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXTRA-CURRICULARS-----------
\section{Open Source \& Competitions}
\resumeSubHeadingListStart
    \resumeItemListStart
      \resumeItem{Hacklytics 2025, GeorgiaTech: Developed an end-to-end Al flight buddy that scores, anticipates and provides relevant real time insights about flights' performances, applying problem-solving skills to real-world data challenges.}
      \resumeItem{Active contributor to Checkmate and several other open source projects, working closely with the maintainers to regulate code reviews, squash bugs and work on developing new features.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}\vspace{2pt}
\begin{itemize}[leftmargin=0.15in, label={}]
    \footnotesize{\item{
    \textbf{Languages \& Frameworks}{: Javascript, Python, Java, Typescript, React.Js, Next.Js, Node.js, Pandas, PyTorch, TensorFlow, Spring, Flask, FastAPI \vspace{2px}} \\
    \textbf{Cloud \& Architecture}{: AWS, Google Cloud, Linux, Git, Docker, Apache Spark, Kubernetes, Kafka, Nginx, Websockets, GitHub Actions \vspace{2px}} \\
    \textbf{Database and QA}{: PostgreSQL, MongoDB, MySQL, Redis, Elastic, Neo4j, Selenium, JUnit, PyTest, Jest}
    }}
\end{itemize}

\end{document}